Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-06-04 sattose/paper.tex
Fixed a mistake in the abstract

\begin{abstract}
Duplication in source code can have a major negative impact on the maintainability of source code, as it creates explicit dependencies between fragments of code. Such explicit dependencies often cause bugs. In this study, we look into the opportunities to automatically refactor these duplication problems for object-oriented programming languages. We propose a method to detect clones that are suitable for refactoring. This method focuses on the context and scope of clones, ensuring our refactoring improves the design and does not created side effects.

>>>>

\begin{abstract}
Duplication in source code can have a major negative impact on the maintainability of source code, as it creates implicit dependencies between fragments of code. Such implicit dependencies often cause bugs. In this study, we look into the opportunities to automatically refactor these duplication problems for object-oriented programming languages. We propose a method to detect clones that are suitable for refactoring. This method focuses on the context and scope of clones, ensuring our refactoring improves the design and does not create side effects.
